---
title: "Software & Data"
author: 
- name: Julien Wollbrett
  affiliation:
  - &SIB Swiss Institut of Bioinformatics (SIB)
  - &DEE Department of ecology and evolution, University of Lausanne, Switzerland
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output:
  html_document:
    toc: true
---

## Software installation

For this practical, you will need R.3.6 or later, which you can download from https://cran.r-project.org/ (if you are using RStudio cloud, that is recommended for this course, this is not necessary) and Bioconductor software version 3.10.

First install BiocManager package, to help you to install and manage packages from Bioconductor project. The code below can be passed directly in the terminal.

```{r eval = FALSE, echo = TRUE}
if (!requireNamespace("BiocManager", quietly=TRUE))
    install.packages("BiocManager")
    BiocManager::install(version = "3.10")
```

Then install the BgeeCall package that will be used for this course, you can downloaded the package from Bioconductor by typing:

```{r eval = FALSE, echo = TRUE}
BiocManager::install("BgeeCall")
```

Some additional packages are used during the course and in that case to install them you just have to type: 

```{r eval = FALSE, echo = TRUE}
BiocManager::install("PACKAGE_NAME")
```

Note: If you want, you can also install RStudio software, which can be download from https://rstudio.com/products/rstudio/download/ to run later your code in your local machine.


## Data

The data used during this course will come from D. melanogaster and consists of :
* 1 RNA-Seq library (fastq files)
* the transcriptome from ensembl 
* the gtf annotation file from ensembl
 
  
