---
title: "Generate calls for one RNA-Seq library"
author: 
- name: Julien Wollbrett
  email: bgee[at]sib.swiss
  affiliation:
    &SIB Swiss Institut of Bioinformatics (SIB), Université de Lausanne 
date: "2020-04-22"
output: workflowr::wflow_html
editor_options:
  chunk_output_type: console
---

```{r load-libs, message = FALSE, warning = FALSE, echo=FALSE}
library(BgeeCall)
```

## Introduction

This page describe how to generate present/absent calls for one RNA-Seq library.

## BgeeMetadata and KallistoMetadata classes

These 2 classes are useful to tune how BgeeCall works. 
No need to create an object of the class BgeeMetada as only default values will be used (last official Bgee intergenic release).  
An object of the KallistoMetadata class has to be created to specify to download kallisto (as it is not installed on RStudio cloud).

```{r kallisto_object}
kallisto <- new("KallistoMetadata", download_kallisto = TRUE)
```

## UserMetadata class

An object of this class has to be created and value of some slots have to be modified to run BgeeCall

```{r user_object, eval=FALSE}
user <- new("UserMetadata", species_id = "NCBI_TAXON_ID", reads_size=READS_SIZE)
user <- setRNASeqLibPath(user, "PATH_TO_RNASEQ_LIBRARY_DIR")
user <- setTranscriptomeFromFile(user, "PATH_TO_TRANSCRIPTOME")
user <- setAnnotationFromFile(user, "PATH_TO_GTF_FILE")
user <- setOutputDir(user, "PATH_TO_OUTPUT_DIR")
user <- setWorkingPath(user, "PATH_TO_WORKING_DIR")
```


## Generate present/absent calls

Now that all objects have been created it is possible to run the generation of present/absent gene expression calls with one unique line of code


```{r run_workflow, eval=FALSE}
output_files_info <- generate_calls_workflow(abundanceMetadata = kallisto, userMetadata = user)
output_files_info
```
```{r fake_output, echo=FALSE}
output_files_info <- NULL
output_files_info$calls_tsv_path <- "path/to/gene_level_abundance+calls.tsv"
output_files_info$cutoff_info_file_path <- "path/to/gene_cutoff_info_file.tsv"
output_files_info$abundance_tsv <- "abundance.tsv"
output_files_info$TPM_distribution_path <- "path/to/gene_TPM_genic_intergenic+cutoff.pdf"
output_files_info$S4_slots_summary <- "path/to/S4_slots_summary.tsv"
output_files_info
```

This command generates a list with a link to 5 generated files.

* _calls_tsv_path_ : path to the file with abundance at gene level and present/absent expression calls
* _cutoff_info_file_path_ : path to the file with metadata about TPM cutoff (TPM cutoff, protein coding genes present, etc.)
* _abundance_tsv_ : path to the kallisto output file with abundance at transcript level
* _TPM_distribution_path_ : path to a PDF file containing a plot of abundance distribution
* _S4_slots_sumary_ : path to the file with value of most important slots of the 3 BgeeCall classes

It is possible to open text files in RStudio with the command file.edit(PATH_TO_FILE).

For example :
```{r show_calls_file, eval = FALSE}
# open calls tsv file
file.edit(output_files_info$calls_tsv_path)
```

